---
title: "DataAnalysis"
author: "Hana Thompson"
date: '2020-01-24'
output: html_document
---

### Analysis of limb measurements dataset created in DataGeneration.Rmd

1. Load required packages
```{r}
library(dplyr)
library(ggplot2)
```

2. Load datafile
```{r}
MData <- read.csv("Data/measurements.csv")
```

3. For efficency, I changed the column names to shorter, 3-letter abbreviations
```{r}
MData <- MData %>% rename(SPS = Species, LWD = Limb.Width, UNW = unitsW, LLN = Limb.Length, UNL = unitsL)
```

4. I added a new data column called Volume that calculates limb volume. 
 * First I have to make sure everything is in the same units by creating a loop to convert mm into cm
```{r}
n <- length(MData$LWD)
for(i in 1:n){
  if(MData$UNW[i] == "mm"){
    MData$LWD[i] <-  MData$LWD[i]/10
    MData$UNW[i] <- "cm"
  }
  if(MData$UNL[i] == "mm"){
    MData$LLN[i] <- MData$LWD[i]/10
    MData$UNL[i] <- "cm"
  }
}
```
* Now I can make a new column for limb volume with units mm^3
* I multiplied Length x Width x Width to get a measure of volume
```{r}
MData <- MData %>% mutate(Volume = LWD*LWD*LLN)
```

5. I created a new vector assigning each species to one of two groups
 * birds that ate while at the bird feeder (BF)
 * birds that took their seed to eat away from the bird feeder (A)
```{r}
feeder <- sample(c("BF", "A"), 10, replace = T, prob = c(0.5, 0.5))
MData <- MData %>% mutate(EAT = feeder)
```

6. I created a table of the mean and standard deviation of length, width, and volume for each group
```{r}
MData %>% group_by(EAT) %>% summarise(mean_L = mean(LLN), sd_L = sd(LLN),
                    mean_W = mean(LWD), sd_W = sd(LWD),
                    mean_V = mean(Volume), sd_V = sd(Volume))
```

7. A plot of limb width and length, with each feeding behvaiour group represented by different colours. 
```{r}
ggplot(MData, aes(x = LWD, y = LLN, colour = EAT)) +
  geom_point(size = 4) +
  theme_classic() +
  scale_y_continuous(name = "Limb length(cm)") +
   scale_x_continuous(name = "Limb width(cm)") +
  scale_colour_manual(name = "Feeding behaviour", labels = c("At bird feeder", "Away from bird feeder"),
                      values = c("mediumpurple2", "seagreen3")) +
   theme(legend.position = "top")
```

8. A plot of limb width and length, but only for species that have above-average volume.
 * first I created a new dataset including only the species that had limb volume above the average of all species
```{r}
newdat <- MData %>% filter(Volume > mean(Volume))
```

 * I then plotted limb width and length using this new dataset
```{r}
ggplot(newdat) +
  geom_point(aes(x = LWD, y = LLN, colour = EAT),
             shape = 17, size = 6) +
  theme_classic() +
  scale_y_continuous(name = "Limb length (cm)") +
  scale_x_continuous(name = "Limb width(cm)") +
  scale_colour_manual(name = "Feeding behaviour", labels = c("At bird feeder", "Away from bird feeder"),
                      values = c("mediumpurple2", "seagreen3")) +
  theme(legend.position = "top")
```

9. A table of Species and Volume including only the species with below-average volume
```{r}
MData %>% filter(Volume < mean(Volume)) %>% select(SPS, Volume)
```









