---
title: "DataGeneration"
author: "Hana Thompson"
date: '2020-01-23'
output: html_document
---

## **Creating a simulated dataset of the limb width and length of several bird species** 

1. I created a vector with all of my species names
```{r}
Species <- c("Cardinalis cardinalis", "Cyanocitta cristata", "Poecile atricapillus", 
             "Sitta carolinensis", "Haemorhous mexicanus", "Haemorhous purpureus", 
             "Turdus migratorius", "Zenaida macroura", "Passer domesticus", "Junco hyemalis")
```

2. I created a vector of 10 values randomly sampled from a normal distribution for limb width
 * I used abs() to ensure that all my values were positive
```{r}
Limb.Width <- abs(rnorm(10, mean = 10, sd = 10))
```

3. I created a vector to randomly assign units (cm or mm) to each width value, each with 50% probability
```{r}
unitsW <- sample(c("mm", "cm"), 10, replace = T, prob = c(0.5, 0.5))
```

4. I repeated steps 2. and 3. for limb length
```{r}
Limb.Length <- abs(rnorm(10, mean = 100, sd = 100))
unitsL <- sample(c("mm", "cm"), 10, replace = T, prob = c(0.5, 0.5))
```

5. I combined all variables into a dataframe and saved to a csv file
```{r}
MyData <- data.frame(Species, Limb.Width, unitsW, Limb.Length, unitsL)
write.csv(MyData, file = "Data/measurements.csv", row.names = F)
```






